Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-30 writeup/gz_hubble_data.tex
Spell-checked. Closes #171.

Images with simulated AGN were classified in the interface in an identical
manner and evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
usng the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim13} uses the simulated AGN host galaxy images for
more reliable identification of bulgeless galaxies hosting AGN in SDSS data.

@@

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels \citep{nie04}. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in the same manner as previous
iterations of Galaxy~Zoo.

@@

Galaxies in GZH show significant changes in the disk/elliptical fraction as a
function of redshift, along with an increasing number of galaxies dominated by
smaller clumps and presumed to be in the process of building up their baryonic
mass through a combination of hierarchical merging and in-situ star formation.
While the majority of scientific interpretation is left to future work, this
paper confirms the decrease in observed bar fraction with increasing redshift
and identifies a new way of selecting clumpy galaxies as a
function of clump multiplicity.

@@

This project made heavy use of the Astropy packages in Python \citep{ast13},
the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and
TOPCAT \citep{tay05,tay11}. Modified code from Nick~Wherry and David~Schlegel
was used to create the JPG images. Figure~\ref{fig:sankey} was generated with
\url{http://sankeymatic.com/}. \citet{hol05} provided valuable assistance
in intepreting \sextractor{} output.

>>>>

Images with simulated AGN were classified in the interface in an identical
manner and evenly distributed with unaltered images of the galaxies.
Volunteers were not explicitly told that the images had been altered during
classification, as the goal was to measure the effect on normal classifications
using the same technique as closely as possible. Following classification, a
classifier could view a page with additional details about each galaxy; where
applicable, these pages contained further information regarding image
modifications. \citet{sim13} uses the simulated AGN host galaxy images for
more reliable identification of bulgeless galaxies hosting AGN in SDSS data.

@@

Stripe~82 single-epoch images were taken directly from the DR7 SDSS SkyServer,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels \citep{nie04}. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in the same manner as previous
iterations of Galaxy~Zoo.

@@

Galaxies in GZH show significant changes in the disk/elliptical fraction as a
function of redshift, along with an increasing number of galaxies dominated by
smaller clumps and presumed to be in the process of building up their baryonic
mass through a combination of hierarchical merging and {\it in-situ} star formation.
While the majority of scientific interpretation is left to future work, this
paper confirms the decrease in observed bar fraction with increasing redshift
and identifies a new way of selecting clumpy galaxies as a
function of clump multiplicity.

@@

This project made heavy use of the Astropy packages in Python \citep{ast13},
the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and
TOPCAT \citep{tay05,tay11}. Modified code from Nick~Wherry and David~Schlegel
was used to create the JPG images. Figure~\ref{fig:sankey} was generated with
\url{http://sankeymatic.com/}. \citet{hol05} provided valuable assistance
in interpreting \sextractor{} output.
